A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-18 appendix.tex
iir filter equations flushed full left
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@647 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{eqnarray}
\label{eq:iirbank}
x_i &[n] \sim& \mathcal{N}[0, 1] \quad \forall \, i, n \nonumber\\\noalign{\vskip 2mm}
y_1 &[n] =& \left(4 \times 10^{-28}\right) x_1[n] - y_1[n-1] + 2 \cdot .99995 \cos \left(\frac{2\pi \cdot 9.103}{16384}\right) y_1[n-2] - .99995^2 y_1[n-3] \nonumber\\\noalign{\vskip 2mm}
y_2 &[n] =& \left(1.1 \times 10^{-23}\right) (x_2[n] - x_2[n-1]) \nonumber\\\noalign{\vskip 2mm}
y_3 &[n] =& \left(10^{-27}\right) x_3[n] - y_3[n-1] + 2 \cdot .999 y_3[n-2] - .999^2 y_3[n-3] \nonumber\\\noalign{\vskip 2mm}
y_4 &[n] =& \left(4 \times 10^{-26}\right) x_4[n] - y_4[n-1] + 2 \cdot .87 \cos \left(\frac{2\pi \cdot 50}{16384}\right) y_4[n-2] - .87 ^ 2 y_4[n-3] \nonumber\\\noalign{\vskip 2mm}
y_5 &[n] =& \left(6.5 \times 10^{-24}\right) x_5[n] - y_5[n-1] - 2 \cdot .45 y_5[n-2] - .45 ^ 2 y_5[n-3] \nonumber\\\noalign{\vskip 2mm}
\; y &[n] =& \frac{3\sqrt{16384}}{4} \left(y_1[n] + y_2[n] + y_3[n] + y_4[n] + y_5[n]\right)
\end{eqnarray}

>>>>

\begin{eqnarray}
\label{eq:iirbank}
\fl x_i &[n] \sim& \mathcal{N}[0, 1] \quad \forall \, i, n \nonumber\\\noalign{\vskip 2mm}
\fl y_1 &[n] =& \left(4 \times 10^{-28}\right) x_1[n] - y_1[n-1] + 2 \cdot .99995 \cos \left(\frac{2\pi \cdot 9.103}{16384}\right) y_1[n-2] - .99995^2 y_1[n-3] \nonumber\\\noalign{\vskip 2mm}
\fl y_2 &[n] =& \left(1.1 \times 10^{-23}\right) (x_2[n] - x_2[n-1]) \nonumber\\\noalign{\vskip 2mm}
\fl y_3 &[n] =& \left(10^{-27}\right) x_3[n] - y_3[n-1] + 2 \cdot .999 y_3[n-2] - .999^2 y_3[n-3] \nonumber\\\noalign{\vskip 2mm}
\fl y_4 &[n] =& \left(4 \times 10^{-26}\right) x_4[n] - y_4[n-1] + 2 \cdot .87 \cos \left(\frac{2\pi \cdot 50}{16384}\right) y_4[n-2] - .87 ^ 2 y_4[n-3] \nonumber\\\noalign{\vskip 2mm}
\fl y_5 &[n] =& \left(6.5 \times 10^{-24}\right) x_5[n] - y_5[n-1] - 2 \cdot .45 y_5[n-2] - .45 ^ 2 y_5[n-3] \nonumber\\\noalign{\vskip 2mm}
\fl \; y &[n] =& \frac{3\sqrt{16384}}{4} \left(y_1[n] + y_2[n] + y_3[n] + y_4[n] + y_5[n]\right)
\end{eqnarray}
